CTest Integration of Sikuli Automated GUI Testing

### 2011-06-09 Documentation/Article.tex
Updated Article.tex.  Need to figure out how to add the screen shot of sikuli script.
Began lead in to integration of CTest paragraph with discussion about Sikuli's Unit Testing feature.

% Feel free to change section titles
\subsection{What is sikuli?}
Sikuli is a programming language that uses screen shot images as variables
and objects in order to automate graphical user interface functions. The
Sikuli program is comprised of an IDE where the user can write scripts that 
include screen shot thumbnails so they can visually track the functions of
their code. The Sikuli Script is built on a Jython (Python for Java platform)
library which uses Python syntax in addition to a number of special Sikuli
functions for aquiring and handling screenshot images and performing mouse,
keyboard actions, the most useful of which are conveniently found as buttons
on the Sikuli IDE.

One of Sikuli's primary uses is the automation of GUI testing for software
developers.

\subsection{Simple of example} % not related to gofigure...

@@

% ------------------------------------------------------------------------
\section{Integration with CTest}
% I'll write it this part

>>>>

% Feel free to change section titles
\subsection{What is sikuli?}
Sikuli is a programming language that uses screen shot images as variables
and objects in order to automate graphical user interface functions. The
Sikuli program is comprised of an IDE where the user can write scripts that 
include screen shot thumbnails so they can visually track the functions of
their code. The Sikuli Script is built on a Jython (Python for Java platform)
library which uses Python syntax in addition to a number of special Sikuli
functions for aquiring and handling screenshot images and performing mouse,
keyboard actions, the most useful of which are conveniently found as buttons
on the Sikuli IDE.  Sikuli then saves a script in a directory with a unique
extension .sikuli.  The directory consists of a the Sikuli script file in a 
html file and as well as a Python script file and includes a list of all the 
screenshot images used in the script.

\subsection{Simple Sikuli example} % not related to gofigure...

@@

% ------------------------------------------------------------------------
\section{Integration with CTest}
% I'll write it this part
One of Sikuli's primary uses is the automation of GUI testing for software
developers.  For GUI testing, it is useful to compartmentalize different software functions and test each unit
individually.  The newest versions of Sikuli come equipped with a Unit Testing feature 
Unit Testing.  Unit Testing can be called using the IDE or by command
line and enables the user to write multiple functions in a script which are
run individually.  At the end of the run, the Sikuli output will tell the user
how many tests ran successfully and which ones failed and where.  To connect this
Unit Testing feature directly to our software, we integrated Sikuli with CTest.
.....
.....
